---
output: github_document
---

# APEVIZ
a suite of data visualization functions I've used in causal effect estimation for program evaluation


## Installation 
```{r eval=FALSE, include=FALSE}
devtools::install_github("https://github.com/cannomb/APEVIZ")
```

### create_plot_metadata() 
This function is mostly used as a part of the create_love_plot() function, however I've made it available to use on it's own as well. It takes in a matchit object (from the MatchIt package) and returns a tibble that includes a column for each variable in the data used by MatchIt, a column for the standard mean difference between the treatment and control group in the unmatched sample, and a column for the standard mean difference between the treatement and control group in the matched sample.

```{r message=FALSE, warning=FALSE}
# Load the MatchIt package
library(APEVIZ)
library(MatchIt)
library(tidyverse)

# Load the Lalonde Dataset 
data("lalonde", package = "MatchIt")

# Create a MatchIt object using the matchit() function
m.out <- matchit(treat ~ age + educ + race + married + nodegree + re74 + re75,
                 data = lalonde,
                 distance = "mahalanobis",
                 replace = TRUE)

create_plot_metadata(m.out)


```

### create_love_plot
This function takes in a matchit object **OR** tibble in the same format (column names included) as the output from the create_plot_metadata() function and returns a love plot as a ggplot2 object. This function includes many options for customization. 

```{r message=FALSE, warning=FALSE, fig.width=10}
create_love_plot(m.out,
                 title = "Results of a mahalanobis distance match on the Lalonde Dataset",
                 subtitle = "")

# change the order of the y axis

default <- create_love_plot(m.out,
                            title = "order_by = unmatched",
                            subtitle = "",
                            axis_text_size = 1)

matched <- create_love_plot(m.out,
                            title = "order_by = matched",
                            order_by = "matched",
                            subtitle = "",
                            axis_text_size = 1)

difference <- create_love_plot(m.out,
                               title = "order_by = difference",
                               order_by = "difference",
                               subtitle = "",
                               axis_text_size = 1)

library(patchwork)

default|matched|difference

```





