---
output: github_document
---

# APEVIZ
a suite of data visualization functions I've used in causal effect estimation for program evaluation


## Installation 
```{r}
devtools::install_github("https://github.com/cannomb/APEVIZ")
library(APEVIZ)
```

### create_plot_metadata() 
This function is mostly used as a part of the create_love_plot() function, however I've made it available to use on it's own as well. It takes in a matchit object (from the MatchIt package) and returns a tibble that includes a column for each variable in the data used by MatchIt, a column for the standard mean difference between the treatment and control group in the unmatched sample, and a column for the standard mean difference between the treatement and control group in the matched sample.

```{r}
# Load the MatchIt package
library(MatchIt)

# Load the Lalonde Dataset 
data("lalonde", package = "MatchIt")

# Create a MatchIt object using the matchit() function
m.out <- matchit(treat ~ age + educ + race + married + nodegree + re74 + re75,
                 data = lalonde,
                 distance = "mahalanobis",
                 replace = TRUE)

create_plot_metadata(m.out)


```

